Competing Bandits:\\The Perils of Exploration under Competition

### 2018-11-05 paper/content/introduction.tex
edit

The interplay between exploration, exploitation and incentives has been studied in other scenarios: incentivizing exploration in a recommendation system,
    \eg \cite{Kremer-JPE14,Frazier-ec14,Che-13,ICexploration-ec15,Bimpikis-exploration-ms17},
dynamic auctions
    (see \cite{DynAuctions-survey10} for background),
online ad auctions, \eg
    \cite{MechMAB-ec09,DevanurK09,NSV08,Transform-ec10-jacm,Amin-auctions-nips13},
and human computation
    \cite{RepeatedPA-ec14,Ghosh-itcs13,Krause-www13}.
Our setting is also closely related to the ``dueling algorithms" framework \cite{DuelingAlgs-stoc11}, but this framework considers offline / full feedback scenarios whereas we focus on online machine learning problems.
\swedit{There is also a line of work on ``dueling bandits" (e.g., \cite{Yue-dueling-icml09, Yue-dueling12}) that also studies a form of competition with MAB problems. However, their framework is fundamentally different from ours in that they study learning from setting ``duels'' between pairs of arms, and we study how learning algorithms compete with each other for data.
}

>>>>

The interplay between exploration, exploitation and incentives has been studied in other scenarios: incentivizing exploration in a recommendation system,
    \eg \cite{Kremer-JPE14,Frazier-ec14,Che-13,ICexploration-ec15,Bimpikis-exploration-ms17},
dynamic auctions
    (see \cite{DynAuctions-survey10} for background),
online ad auctions, \eg
    \cite{MechMAB-ec09,DevanurK09,NSV08,Transform-ec10-jacm,Amin-auctions-nips13},
and human computation
    \cite{RepeatedPA-ec14,Ghosh-itcs13,Krause-www13}.
Our setting is also closely related to the ``dueling algorithms" framework \cite{DuelingAlgs-stoc11}, but this framework considers offline / full feedback scenarios whereas we focus on online machine learning problems.
\swedit{There is also a line of work on ``dueling bandits" (e.g., \cite{Yue-dueling-icml09, Yue-dueling12}) that also studies a form of competition with MAB problems. However, their framework is fundamentally different from ours in that they study learning from setting up ``duels'' between pairs of arms, and we study how learning algorithms compete with each other for data.
}
